\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.8em}

\begin{document}

{\Large \textbf{Deep Akbari}}\\
Tampa, FL\\
\href{mailto:ackberrie@gmail.com}{ackberrie@gmail.com} \;|\; 813-521-9904 \;|\;
\href{https://www.linkedin.com/in/deep-akbari/}{LinkedIn} \;|\;
\href{https://github.com/ackberry}{GitHub}

\today

Hiring Manager\\
Engineering Team

Dear Hiring Manager,

I am applying for a software engineering internship where I can contribute to product delivery while continuing to build strong backend and AI engineering fundamentals. My recent work has focused on production-minded full-stack systems, LLM-backed workflows, and measurable engineering outcomes in internship and research settings.

At CacheAi, I deployed an LLM-based user scoring pipeline for a job board that automated ranking for more than 200 users and replaced manual evaluation with a reliable, repeatable process. I also built a Python ETL workflow to process data from over 2{,}000 U.S. engineering schools, improving ranking consistency and reducing operational effort. In research at USF RARE Lab, I co-authored an ACM HRI 2026 companion paper and helped build a Linux-based conversational robotics stack integrating speech, LLM, and TTS components; this work improved task success by 35\% in testing.

Alongside internship experience, I have built and shipped projects with React, Node.js, TypeScript, Python, and cloud tooling. These include transcript analysis and semantic search pipelines, REST APIs optimized for sub-200ms response times, and CI workflows using GitHub Actions. I value clear ownership, strong communication, and practical iteration, and I would bring that approach to your team from day one.

Sincerely,

Deep Akbari

\end{document}
