\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.8em}

\begin{document}

\textbf{Deep Akbari}\\
813-521-9904\\
ackberrie@gmail.com\\
\href{https://www.linkedin.com/in/deep-akbari/}{LinkedIn} | \href{https://github.com/ackberry}{GitHub} | \href{https://ackberry.club/}{Portfolio}

\vspace{1em}

\today

\vspace{1em}

Twilio Hiring Team\\
Software Engineer Intern Program\\
Dublin, Ireland

\vspace{1em}

Dear Hiring Manager,

I am writing to express my strong interest in the Software Engineer Intern position for Twilio's 12-week summer program beginning in June. As a Computer Science student at the University of South Florida with demonstrated experience in distributed systems and real-time applications, I am excited to contribute to Twilio's mission of delivering innovative communications solutions while advancing my technical expertise in your cloud-native environment.

My technical background directly addresses Twilio's core requirements for designing, developing, and deploying scalable software solutions. I have built full-stack systems supporting 100+ concurrent users with sub-200ms API latency, demonstrating proficiency in the high-availability architectures essential for next-generation communications. My deployment of an LLM-based scoring pipeline using the Gemini API, which automated ranking processes for 200+ users, exemplifies my ability to operate distributed systems at scale while solving latency and quality challenges in cloud environments.

I possess strong experience with technologies central to Twilio's infrastructure, including Python, distributed data processing, and testing methodologies. My Python ETL system for processing data from 2,000 U.S. engineering schools replaced manual workflows with automated solutions, while my PostgreSQL-backed REST APIs achieved consistent sub-200ms query performance. I have implemented comprehensive CI/CD pipelines using GitHub Actions and developed robust testing frameworks, directly supporting Twilio's emphasis on code quality, agile development, and systematic deployment practices.

Twilio's commitment to diverse experiences and inclusive innovation particularly resonates with me. As Technical Lead of Google Developer Group, I have facilitated collaborative development environments and mentored emerging developers---experience that aligns with Twilio's culture of learning and knowledge sharing. I am eager to contribute my entrepreneurial mindset and passion for emerging technologies to help Twilio continue revolutionizing global communications infrastructure.

Thank you for your consideration. I look forward to discussing how my technical skills and collaborative approach can contribute to Twilio's continued success.

Sincerely,

Deep Akbari

\end{document}